\speculake: Hiding Malware in Speculative Execution

### 2018-12-07 paper/architecture.tex
clean up description of uops

We find that when executing speculatively, the number of instructions completed
is rarely limited by cache miss duration. Instead
ROB size and processor mechanisms for resolving
data dependencies define an upper boundary of approximately 150
instructions\footnote{While \texttt{nop} is able to execute up to the full 220
ROB capacity, instructions that do useful work (and/or use multiple $\mu$ ops) cannot reach this limit}.

>>>>

We find that when executing speculatively, the number of instructions completed
is rarely limited by cache miss duration. While data dependency and ROB size
have an effect on the number of instructions that can be executed speculative
Figure~\ref{fig:spec-capacity-np} demonstrates that the number of $\mu$-ops of
the instructions is the major limiting factor that define an upper boundary of
approximately 150 instructions\footnote{While \texttt{nop} is able to execute up
to the full 220 ROB capacity, instructions that do useful work (and/or use
multiple $\mu$ ops) cannot reach this limit}.
